An Executable Formal Semantics For A Functional Actor Language

### 2017-12-19 paper/paper.tex
syntax and reduction contexts

\section{The Actor Language in K}
\subsection{Configuration}
\subsection{Syntax and Evaluation Contexts}
\subsection{Semantics}
\subsection{In-depth Example}

>>>>

\section{The Actor Language in K}

\subsection{Configuration}

\subsection{Syntax and Reduction Contexts}
Syntax for constructs in K is specified using BNF notation. For example, we
specify values (where reduction can no longer happen) as
\begin{verbatim}
  syntax Val  ::= CVal                                    
                | "lambda" "(" Id "," Exp ")" [binder]
                | "pr" "(" Val "," Val ")"
\end{verbatim}
where \texttt{CVal} represents the communicable values, \texttt{lambda}
represents lambda expressions, and \texttt{pr} represents pairs of values.  The
\texttt{binder} attribute is used in K's backend for substitution, as it
specifies that \texttt{Id} is bound in the term \texttt{Exp}.

In K, we can also use syntax to express contexts in which reduction is allowed.
In the actor language, reduction contexts are separately defined to specify
evaluation order of expressions. For example, the set of reduction contexts for
functions in the actor language are specified as
\[ \mathbb{F}_{n+m+1}(\mathbb{V}^n,\mathbb{R},\mathbb{E}^m) \]
This states that the argument of a function can be evaluated only when the first
$n$ arguments have already been evaluated. In K, this is simply specified using
the attribute \texttt{seqstrict} which states the arguments of a syntactic
construct are evaluated in order. Addition, for example, is specified in K as
\begin{verbatim}
syntax Exp ::= "add" "(" Exp "," Exp ")" [seqstrict]
\end{verbatim}
Note nothing beyond the appropriate strictness attribute is needed to specify
reduction contexts in K for this language.

For the branching, we would like to only specify that only the first argument
should reduce to a value, to avoid reduction in the branch we end up not taking.
In the actor semantics from~\cite{}, this is accomplished with the following:
\[ \texttt{if}(e_0, e_1, e_2) \;\;\;\text{abbreviates}\;\;\; \texttt{app}(\texttt{br}(e_0, \lambda z.e_1, \lambda z.e_2), \texttt{nil}) \;\;\;\text{for $z$ fresh} \]
Notice that the second and third arguments in the branch construct are lambda
expressions, which are values, and thus will not be reduced any farther. In our
K semantics, we emulate this, but we could also define \texttt{br} directly to
be only strict in the first argument as follows:
\begin{verbatim}
syntax Exp ::= "br" "(" Exp "," Exp "," Exp ")" [strict(1)]
\end{verbatim}
Strictness constructs like this avoid unnecessary syntactic sugar, and cleanly
specify most reduction contexts one would require.

\subsection{Semantics}

\subsection{In-depth Example}
